---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# taskmanager

<!-- badges: start -->
<!-- badges: end -->

taskmanager allows users to create, edit, and organize a list of tasks a user aims to complete. It's similar to a to do list.

## Installation

You can install the development version of taskmanager from [GitHub](https://github.com/) with:


```{r}
# install.packages("devtools")
devtools::install_github("hannalee809/taskmanager")
```

## Example

This is a basic example showing you how to create a task list:

```{r eval=FALSE}
library(taskmanager)

add_task()
```

You can delete, edit, organize, summarize, split, and find a task with the functions below:

```{r eval=FALSE}

# add task to existing data frame
add_task(tasks_df)

delete_task(tasks_df)

edit_task(tasks_df, column_num, "task_description")

find_task(tasks_df, "task_description")

organize_tasks(tasks_df)

split_tasks(tasks_df, column_num, "task_desc_under_column_num")

summary_tasks(tasks_df)
```

add_task() can take the input of a df of a task list

delete_task() takes in the name of the df of a task list

edit_task() takes in the name of the df of a task list, the column number of the task you'd like to edit, and the task description in "quotes"

find_task() takes in the name of the df of a task list and the description of the task in "quotes"

organize_tasks() takes in the name of the df of a task list

split_tasks() takes in the name of the df of a task list, the column you'd like to split by, and the description of the task below the column you'd like to split by in quotes.

summary_tasks() takes in the name of the df of a task list

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.
